Conjure: Summoning Proxies from Unused Address Space

### 2019-09-24 paper/paper.tex
Update paper.tex

@@

\subsubsection{IPv4}
While \scheme composes well with IPv6, we can also support IPv4, with some
careful caveats. First, in IPv4, there are substantially fewer addresses,
allowing censors to easily \textbf{enumerate network prefixes} that pass by the ISP
station to look for legitimate sites to whitelist. To address this, \scheme
phantom hosts are firewalled from all IPs other than the client that registered
them. Thus, censors would not see them in an enumerating scan from a single
vantage point before registration (when they do not exist), and blocking hosts
not seen in such a scan would block legitimate hosts that firewalled themselves
off from all but a few IPs. % Such firewall behavior is a best practice for...
Censors could attempt to scan the network from \emph{all} potential client
vantage points, by co-opting client IPs to perform scans---a behavior previously
observed by the Great Firewall of China to scan for Tor bridges~\cite{ensafi-tor}.
To prevent this, for IPv4 \scheme, we dynamically generate the TCP port of the
phantom host (along with its IP) from the registration seed, which further makes
exhaustive scans infeasible:
a censor that must enumerate from the vantage point of a /10 of client IPs (4~million IPs)
to a /16 (65K IPs) of potential phantom proxies on each of 65K potential ports would take nearly
50~years of scanning with ZMap at 10~Gbps. We note that while the use of
non-standard ports could potentially be suspicious, several successful
circumvention tools---including Psiphon~\cite{psiphon} and
\texttt{obfs4}~\cite{obfs4}---use random ports on their obfuscated protocols.
Finally, we note that censors that whitelist either standard ports or discovered
hosts from enumerations scans would over-block new services that came online after
their scans.

A second problem in IPv4 \scheme is that the limited range of IPs (and ports)
makes it possible for a censor to \textbf{pre-image the hash} used to derive the phantom
address from the seed. Even with the /16 of IPs and all 65K ports, a censor need
only test an expected $2^{32}$ possible seeds to find one that would allow it
to register for that phantom address. The censor could then register a suspected
address, and see if it provides proxy access. If it does, the censor learns
there is no legitimate service there, and can block it. To combat this, we
allow only a single client to register for a particular phantom address at a
time. A censor could attempt to register all addresses in an attempt to deny
proxy service to legitimate users, but this would be easily observed at the
registration system, where rate limits via client puzzles or account-based fees
could be enforced.

Finally, legitimate \textbf{IPv4 addresses density} is much higher than IPv6,
increasing the potential for users to accidentally register seeds that derive
phantom addresses corresponding to live hosts. To address this, the station
sends probes to potential IPv4 phantom hosts during registration, and ignores the
registration if a real host responds. Censors that try to register specific
phantom proxies will be unable to distinguish if another user has registered it
or a legitimate host is there, as in both cases we ignore the censor's
registration. This also serves to prevent abuse by attackers that attempt
to use the \scheme station to interfere with legitimate services.

@@

\subsubsection{IPv6 address entropy}
\FigIpBits

In IPv6 \scheme, we no longer need to worry about address enumeration or
pre-image attacks. Our ISP routes a /32 IPv6 prefix, which provides $2^{96}$ potential
phantom host IP addresses. However, IPv6 addresses often have long runs of 0
bits in them, and rarely use all 128-bits equally.
For instance, google.com has the address
%\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}, which only has 24 bits set to 1.
Censors might try to use this observation and block high entropy IPv6 addresses.

>>>>

\subsection{Performance}

@@

\subsubsection{IPv4}
While \scheme works best with IPv6, it can also support IPv4, with some
careful caveats.

First, in IPv4, there are substantially fewer addresses,
allowing censors to potentially \textbf{enumerate all the network prefixes}
that pass by the ISP station, compose the list of innocuous sites,
and block other websites, as they are being summoned by \scheme.
To address this, \scheme
phantom hosts are firewalled from all IPs other than the client that registered
them, providing a reason why the address hasn't been seen in an enumerating scan,
conducted by a censor from a single vantage point.
Censors could attempt to scan the network from \emph{all} potential client
vantage points, by co-opting client IPs to perform scans---a behavior previously
observed by the Great Firewall of China to scan for Tor bridges~\cite{ensafi-tor}.
To prevent this, for IPv4 \scheme, we dynamically generate the TCP port of the
phantom host (along with its IP) from the registration seed, which further makes
exhaustive scans infeasible:
a censor that must enumerate from the vantage point of a /10 of client IPs (4~million IPs)
to a /16 (65K IPs) of potential phantom proxies on each of 65K potential ports would take nearly
50~years of scanning with ZMap at 10~Gbps. We note that while the use of
non-standard ports could potentially be suspicious, several successful
circumvention tools---including Psiphon~\cite{psiphon} and
\texttt{obfs4}~\cite{obfs4}---use random ports on their obfuscated protocols.
Finally, we note that censors that whitelist either standard ports or discovered
hosts from enumerations scans would over-block new services that came online after
their scans.

A second problem in IPv4 \scheme is that the limited range of IPs (and ports)
makes it possible for a censor to \textbf{pre-image the hash} used to derive the phantom
address from the seed. Even with the /16 of IPs and all 65K ports, in order to
find a seed for any desired address a censor
needs to only test an expected $2^{32}$ possible seeds.
The censor could then register a suspected
address, and see if it provides proxy access. If it does, the censor learns
there is no legitimate service there, and can block it. To combat this, we
allow only a single client to register for a particular phantom address at a
time. A censor could attempt to register all addresses in an attempt to deny
proxy service to legitimate users, but this would be easily observed at the
registration system, where rate limits via client puzzles or account-based fees
could be enforced.

Finally, legitimate \textbf{IPv4 addresses density} is much higher than IPv6,
increasing the potential for users to accidentally register seeds that derive
phantom addresses corresponding to live hosts. To address this, the station
sends probes to potential IPv4 phantom hosts during registration, and ignores the
registration if a real host responds. Censors that try to register specific
phantom proxies will be unable to distinguish if another user has registered it
or a legitimate host is there, as in both cases we ignore the censor's
registration. This also serves to prevent abuse by attackers that attempt
to use the \scheme station to interfere with innocuous services.

@@

\subsubsection{IPv6}
\FigIpBits

In IPv6 \scheme address enumeration and pre-image attacks are infeasible due to a large amount of
potential IP addresses.
Our ISP routes a /32 IPv6 prefix, which provides $2^{96}$ potential
phantom host IP addresses. However, IPv6 addresses often have long runs of 0
bits in them, and rarely use all 128-bits equally.
For instance, google.com has the address
%\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
\texttt{2607:f8b0:400f:806::2004}, which only has 24 bits set to 1.
Censors might try to use this observation and block high entropy IPv6 addresses.
